Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-24 doc/PRF2022/PRF_main.tex
figs and refs

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f), the relative enclosed area $A/A_0$
  decreases over time. The inset shows the relative length $L/L_0$ which
  remains nearly constant with small fluctuations. The inset and main
  panel have the same horizontal axis.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

@@

For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculate the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
steady-state that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
words, the flow pattern is non-monotonic in the cell size $\lambda$.

@@

Scaling laws for the ``virial viscosity'', the nonhydrodynamic part of the
relative viscosity in steady shear, have 
been determined experimentally~\citep{PhysRevFluids.5.053302}. 
Other simulation studies have investigated the rheology of strain-hardening
capsules as a function of membrane inexstensibility
using the three-dimensional immersed boundary method~\cite{aouane_scagliarini_harting_2021},
dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
and shown how shear
thickening in systems with widely different particle properties stems 
arise when adhesion forces bring particles into frictional contact
~\cite{PhysRevFluids.7.054302}. Within this context, membrane inexinsibility
in the case of Type I amphiphiles and adhesion in general 
can be inferred from the functional relationships between free energy
and displacement in Figure~\ref{fig:fsummary}(c), for example.

>>>>

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), the relative change in $\dot \gamma_*$ is linear in the
  relative change of the tension parameters $\gamma$ and $M$ with slope
  $1$. Additionally, the relative change in $\dot \gamma_*$ has slope
  $-2$ with respect to the relative change in the length parameters $c$,
  $\rho$, and $\rho_0$. Panels (b)--(e) show the tank-treading
  configuration of a vesicle bilayer the configurations with streamlines
  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
  respectively. In panel (f),
  inset, the relative enclosed area $A/A_0$
  for the four cases in panels (b)--(e) decays to a steady state.
  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
  in $\lambda$.} 
%  \todo[inline]{We propose to relate panel (f) to the pressure drops
%  across the JP vesicles. Also, panel (a) should be its own figure, and
%  (b)--(e) can be their own figure, but with darker stream lines. Also,
%  should not be talking about tank treading, but rather about sliding
%  between layers, and how they are affected by the correlation between
%  the bilayer location and the TG cell boundary. This correlation also
%  somehow determines the shape. Can count the number of partial TG cells
%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
%  (e) has 1 cell.}
\end{figure}

@@

For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculated the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area achieves a
steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (data not shown). In other
words, the flow pattern is non-monotonic in the cell size $\lambda$.

@@

Scaling laws for the ``virial viscosity'', the nonhydrodynamic part of the
relative viscosity in steady shear, have 
been determined experimentally~\citep{PhysRevFluids.5.053302}. 
Other simulation studies have investigated the rheology of strain-hardening
capsules as a function of membrane inexstensibility
using the three-dimensional immersed boundary method~\cite{aouane_scagliarini_harting_2021},
studied dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
and shown how shear
thickening in systems with widely different particle properties stems 
arise when adhesion forces bring particles into frictional contact
~\cite{PhysRevFluids.7.054302}. Within this context, membrane inexinsibility
in the case of Type I amphiphiles and adhesion in general 
can be inferred from the functional relationships between free energy
and displacement in Figure~\ref{fig:fsummary}(c), for example.
